Unsupervised Acquisition of Comprehensive Multiword Lexicons \\ using Competition in an $n$-gram Lattice

### 2017-05-12 reviewer_response.txt

> Where I had trouble was with the details of the model. First of all, much ofit seemed to be ad hoc; even accepting the notion of LPR from prior work,
there are many heuristic (or at least not obviously natural) choices made to
operationalize the general lattice idea mathematically. Second, even if the
model is reasonable, it is not entirely clear how the different parts fit
together into an optimization problem. There is mention of a parameter C;
and there is a notion of nodes being activated or not (I don’t think
notation is introduced for these binary variables, though it would be
appropriate). Are these the only things that have to be tuned? Is the
calculation of explainedness deterministic based on these? There is a greedy
search to optimize explainedness of the nodes in the lattice, subject to
various heuristics. Presenting a formal algorithm for the optimization may
clarify things considerably.

We have reorganized the method section and added an explicit objective function, which should help with some of your problems. In terms of the central optimization problem, the only variables are exactly the on/off status of each node, and, if we exclude the parameters used in the creation of the lattice (e.g. the n-gram frequency threshold) and those involved in the efficiency restrictions, the only (hyper)parameter in the optimization is C; we have tried to make this more clear. We have also included psuedocode for optimization algorithm. With regards to the ad hoc parts of the model, we have added a discussion separating the core aspects of the model from some of the more ad hoc choices made in the particular instantions of component functions (such as clearing), making it clear that we believe these can potentially be improved on (both in terms of performance as well as mathematical elegance), and that our primary purpose here is to show that overall architecture of the model is a promising one.

> I think it would also be worth discussing how the lattice model relates back to the cognitive/psychological literature. Would you predict (or are you
aware of any evidence) that node interactions such as covering, clearing,
and overlapping have an analogue in human language processing? Do any of the
design decisions intentionally sacrifice cognitive plausibility for
engineering reasons?

In general, we did not consider cognitive plausibility when creating the model, and we are certainly making no claims as such. For starters, our model makes use of more data than a human being could possibly read in a lifetime; it is clear we identify FS with far less evidence than our model requires. With space, we could discuss our model in the context of the more cognative aspects of the theory of formulaic sequences as proposed by Wray, but given that this wasn't a focus in the development of the model, we think it is really too much of a digression to justify.

> - After the equation for LPR, it would be good to give the intuition:
choosing a context span such that w_i is more likely given its context words
than its context POS tags.

This was removed from an earlier draft for space, and we've added back in.

>- Inter-annotator agreement is surprisingly high. Could you elaborate on
Wray’s criteria for FS that were applied by annotators?

Your surprise about the the Kappa being high is based on a misunderstanding: the kappa number reported in the table is after filtering to remove borderline cases (i.e. it is the kappa for the final test set, not the original sampling). To avoid confusion, we've added the original kappa score which is quite a bit lower. Your intution is correct that there is significant subjectivity to FS identification (more so than MWE annotation), and as such we would never rely on a single annotator for building a FS test set. We have not added more information about Wray's criteria; though it provide a starting point for annotation, more relevant to achieving reasonable agreement are the specific annotation guidelines which we created. Presenting them in the paper would be too much of a digression, but we promise to make them public.

> - I would like to see qualitative analysis of the sequences that were
identified as formulaic (or not) by annotators/the method. E.g.: How many of
them are syntactic constituents? Are there a wide variety of grammatical
kinds of expressions? Are high-frequency as well as low-frequency sequences
detected? What is the distribution in terms of length? What kinds of gapped
sequences are there? It would be nice to see some examples.

In the discussion, we have added a thorough analysis of specific examples and some statistics, including most of the infromation you ask for.

> - Related to the previous point: While noting the distinction between FS and
MWEs, is it perhaps worth measuring recall against MWE datasets? Most MWEs
apart from proper names should count as FS, right?

Do you mean as a way of evaluating different systems built on the same corpus, or just to get a sense of coverage more generally? One central problem with using recall for evaluation is that in order to make it fair, there must be some control of the size of the lexicon. Neither our system nor our best performing competitors are ranking models, none of them offer an easy or fair way to simply take the best N words and look at recall. And even if they did, there's other kinds of biases that would come into play: for instance, PMI and similar metrics do well with rare terms that correspond well to the MWE lexicon of WordNet, for instance, which (at the type level) is dominated by certain kinds of terminology (biomedical terms, particularly) which are not really used outside a very specific community. This relates to a more fundamental problem with the idea of using recall in external lexicons as any kind of useful measure: we could not expect any particular corpus (even a very large one) to do justice to the full range of FS/MWE for a language, since most of which appear regularly only within specific genres. For example, we could not expect to build a good lexicon of English verb-particle constructions from a biomedical corpus, because many are too informal to be appropriate for that genre (e.g. "mess up"). We have added more discussion of the genre-specificity of FS to the paper, as part of the qualitative analysis

Though it perhaps does not directly address your comment (since it doesn't involve an external MWE dataset), we were nonetheless inspired to include an analysis of the recall of MWE vs. non-MWE FS in the context of our existing test sets.

>Typographical issues:

- The ovals in Figure 1 and the edges in Figure 2 show up for me on screen
(OS X Preview) but not when printed.
- “pairing down” -> paring down
- “what is typically considered MWE” -> are…MWEs
- “could be useful addition” -> *a* useful addition
- "When the minLPR metric is 1 (crresponding to the case of the syntactic
content predicting": content -> context?

 We have addressed these typos, thanks.
